Staged Abstract Interpreters

### 2019-09-11 paper/50_stageabs.tex
typo

\paragraph{What has been eliminated?} In the generated code, all the
primitive operations (such as @eval@, @fix@, @ap_clo@, etc.) and monadic
operations (such as @flatMap@ and @map@) are eliminated. The residual program
consists of statements and expressions that purely manipulate the environment,
store, and two caches, whose underlying representations are all @Map[K,V]@.
We also have several operations on tuples and lists, which are residualized from
the internal code fragments of the monads.

>>>>

\paragraph{What has been eliminated?} In the generated code, all
primitive operations (such as @eval@, @fix@, @ap_clo@, etc.) and monadic
operations (such as @flatMap@ and @map@) are eliminated. The residual program
consists of statements and expressions that purely manipulate the environment,
store, and two caches, whose underlying representations are all @Map[K,V]@.
We also have several operations on tuples and lists, which are residualized from
the internal code fragments of the monads.
